Proposed Solution

### 2016-01-27 design.tex
whcih errors

>>>>

We are not quite machine learning because we use more formal reasoning.
This let's us have a nice garuntee that while we have false positives, but not false negatives.

\forall errors, error \in report
not \forall report r \in error

Another benefit is that, unlike machine learning algorithms, such as nueral nets, we can actually see the source of errors and the systems reasoning about why a line should be considered an error.
In nueral nets, we just get a boolean value, and the mechanics of the system are entirly lost. 
The language model is then recoverable and editable.

The system is also flexible so that changes to the algorithm can be made at a high level.
